A large and variable leading tail of Helium in a sub-Saturn undergoing runaway inflation

### 2023-06-05 paper/paper1/ms.tex
Add a conclusion

>>>>

We have presented a multi-year spectroscopic survey of HAT-P-67~b, a low density, heavily irradiated Saturn-mass (or lower) planet.  We identified a large leading tail, with a much weaker trailing tail, which we found to be consistent with preferential dayside mass loss.  HAT-P-67~b stands out as an outlier in the mass-radius plane, which we examine through the lens of different mechanisms for anomalous heating.  Both XUV irradiation and Ohmic dissipation predict runaway inflation for such inflated hot Saturns, and we quantitatively weigh these two scenarios, finding XUV irrdation as more straightforwardly predictive of the overall demographic population of exoplanets observed to date.

We report in-transit line profile variability, which we attribute to the delicate interplay of planetary and stellar winds.  We identify several avenues for future work, including additional monitoring of the line profile variability to probe the stellar-and-planetary wind interaction.  The large signal should be perceptible in other spectral tracers, such as metal lines in the UV.  We offer a list other planets that may be likely to exhibit mass loss under the Ohmic Dissipation and XUV irradiation scenarios.
